Exploratory_Analysis

### 2021-04-22 Code/Exploratory_Analysis.Rmd
commit exploratory analysis 4/22

# Load Packages
library(plyr)
library(stringr)
library(tidyr)
library(lubridate)
library(tidyverse)
library(agricolae) 
library(dplyr)
library(viridis)
library(RColorBrewer)
library(colormap)
library(sf)
library(leaflet)
library(mapview)
library(raster)
library(sp)
library(rgdal)
library(cowplot)
#install.packages("rnaturalearth")
#install.packages("rnaturalearthdata")
library(rnaturalearth)

@@

```
__Condition of Trail __      | __Total Amount__
--------------------         |---------------------------
Poor (P)                     | 27,218
Medium (M)                   | 13,666
Heavy (H)                    | 26

@@

##filter for dates from 02-28-2018 -- 03-10-2018
subset_trails <- tracklogs %>%
  filter(date == "2018-02-28")

#CRS=WGS84 = 4326 or UTM zone 32S = 32732

#convert to sf and include crs (I used UTM zone 32S and coord columns)
subset_sf <- st_as_sf(subset_trails, crs = 4326, coords = c("lat", "lon"))

#transform to UTM
trails_UTM <- st_transform(subset_sf, crs=32633)

#Plot the data to see the trails - the projection is off by a little 
Trail_map1 <- mapview(trails_UTM)
  Trail_map1

@@

## ANALYSIS
```{r plots by width}

name_plots <- ggplot(tracklogs, aes(x = use_cha, y = use_num)) +
  geom_boxplot(fill = "darkblue") + ggtitle("Trail type by width") + xlab("Type of Trail") + ylab("Width of trail") + mytheme

print(name_plots)

```{r boxplots trail by widths}

##boxplot width of poor trails
PT_plot <- ggplot(Poor_trails, aes(x=use_cha, y=use_num)) +
  geom_boxplot(fill = "seagreen") + 
  ggtitle("Poor Troddened Trail by widths") + 
  xlab("Amount of use") + 
  ylab("Width of trail") + ylim(35, 55) + mytheme
print(PT_plot)

@@

tstack

##boxplot frequency - number of days a trail was used

ggplot(tracklogs, aes(x=date, fill = use_cha)) + 
  geom_bar() + 
  scale_x_date(date_breaks ="10 days", date_labels = "%Y-%m-%d", 
          guide = guide_axis(angle = 45)) + 
  ggtitle("Amount of Trails by day") +
  mytheme

@@

```{r model - Analysis}
#is the width of the trail significant on the frequency of use?

#do any of the variables (lat, lon, use_num) explain use_cha
mod_1 <- lm(data = tracklogs, factor(use_cha) ~ lat + lon + use_num)
  summary(mod1)

>>>>

# Load Packages
library(plyr)
library(stringr)
library(tidyr)
library(lubridate)
library(tidyverse)
library(agricolae) 
library(dplyr)
library(viridis)
library(RColorBrewer)
library(colormap)
library(sf)
library(leaflet)
library(mapview)
library(raster)
library(sp)
library(rgdal)
library(cowplot)
#install.packages("PMCMRplus")
library(PMCMRplus)
#install.packages("rnaturalearth")
#install.packages("rnaturalearthdata")
library(rnaturalearth)

@@

```
__Condition of Trail __      | __Total Amount__
--------------------         |---------------------------
Poor (P)                     | 27,218
Medium (M)                   | 13,666
Heavy (W)                    | 26

@@

##filter for dates from 04-15-2018
subset_trails <- tracklogs %>%
  filter(date == "2018-04-15")

##subset for each type of trail for 04-15-2018
subset_poor <- Poor_trails %>%
  filter(date == "2018-04-15")

subset_med <- Med_trail %>%
  filter(date == "2018-04-15")

subset_heavy <- Heavy_trail %>%
  filter(date == "2018-04-15")

#CRS=WGS84 4326

#convert to sf and include crs
subset_sf <- st_as_sf(subset_trails, crs = 4326, coords = c("lon", "lat"))

subset_poor_sf <- st_as_sf(subset_poor, crs = 4326, coords = c("lon", "lat"))
subset_med_sf <- st_as_sf(subset_med, crs = 4326, coords = c("lon", "lat"))
subset_heavy_sf <- st_as_sf(subset_heavy, crs = 4326, coords = c("lon", "lat"))

#Plot the data to see the trails for 2-28-18 
Trail_map1 <- mapview(subset_sf, color = use_cha)
  Trail_map1

#Plot so each type of trail is a different color on 4- 15-18 so heavy is included 
Trail_map2 <- 
mapview(subset_poor_sf, color = "darkseagreen3", col.regions = "darkseagreen4") +
  mapview(subset_med_sf, color = "coral2", col.regions = "coral3") +
    mapview(subset_heavy_sf, color = "lightblue", col.regions = "darkblue")
Trail_map2
```

## ANALYSIS
```{r plots by width}
##Use this plot instead of stacked

width_plots <- ggplot(tracklogs, aes(x = use_cha, y = use_num)) +
  geom_boxplot(fill = "lightblue") + ggtitle("Trail type by width") + xlab("Type of Trail") + ylab("Width of trail (cm)") + mytheme

print(width_plots)

boxplot(use_num ~ use_cha, data = tracklogs)
boxplot(count ~ use_cha, data = tracklogs)

@@

```{r boxplots trail by widths}
## NOT USING THESE STACKED PLOTS
##boxplot width of poor trails
PT_plot <- ggplot(Poor_trails, aes(x=use_cha, y=use_num)) +
  geom_boxplot(fill = "seagreen") + 
  ggtitle("Poor Troddened Trail by widths") + 
  xlab("Amount of use") + 
  ylab("Width of trail (cm)") + ylim(35, 55) + mytheme
print(PT_plot)

@@

tstack
```

```{r boxplot # of days}
##boxplot count - number of days a trail was used

freq_plot <- ggplot(tracklogs, aes(x=date, fill = use_cha)) + 
  geom_bar() + 
  scale_fill_manual(values = c("darkseagreen3", "deepskyblue3", "deeppink")) +
  scale_x_date(date_breaks ="10 days", date_labels = "%Y-%m-%d", 
          guide = guide_axis(angle = 45)) + 
  (theme(legend.position = "right", 
        legend.text = element_text(size = 12), legend.title = element_text(size = 12))) +
  labs( y = "Count", 
        x = "Date", 
        title = "Number of Trail Points per Day", 
        fill = "Use of Trail") +
  mytheme

print(freq_plot)

@@

```{r model - Analysis}

##which trails have a significantly different width from one another 
mod3 <- lm(data = tracklogs, use_num ~ use_cha)
  summary(mod3)
  TukeyHSD(aov(mod3))
  plot(TukeyHSD(aov(mod3)))

  plot.design(use_num ~ use_cha, data = tracklogs)

  #results W-M, W-P= sig, P-M=not sig
